Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2016-11-14 apj.tex
making the paper better.

\color{blue}
There remains degeneracies in the model.  One is illustrated by the  transformations $\Delta \rightarrow \Delta  + \epsilon_\Delta$,
 $\gamma^0 \rightarrow \gamma^0  + \epsilon_{\gamma^0}$, $\gamma^1 \rightarrow \gamma^1 + \epsilon_{\gamma^1}$under the condition
$$
\epsilon_\Delta  +  \epsilon_{\gamma^0} k_0+  \epsilon_{\gamma^1} k_1=0,
$$
i.e.\ shifts in the global coefficients $\gamma$ can be compensated by shifts in $\Delta$ for each supernova while maintaining 
$\langle \Delta \rangle=0$.
Another degeneracy is illustrated by $k_0 \rightarrow k_0 + (EW_{Ca}-\langle EW_{Ca}\rangle)\epsilon$,
$\alpha \rightarrow \alpha - \gamma \epsilon$, $c \rightarrow c + \langle EW_{Ca}\rangle \epsilon$, i.e. the
linear external terms can leak into the linear spectral feature corrections.
These degeneracies are not broken within the model, but rather are constrained by the priors, for which the
per-supernova parameters
$\Delta$, $EW$, $\lambda$, $k$ are uncorrelated.
\color{black}

@@

The \citet{1989ApJ...345..245C} dust law can be expressed as a two-parameter linear model
\begin{equation}
A_X = a(X)  A_V + b(X) E(B-V).
\end{equation}
The \citetalias{1999PASP..111...63F} model is approximately described by a linear model with
the above form:
\color{red}
for the case of
$R^F_V=2.5$ and $A^F_V=0.1$,
and the measurement of the updated
\citet{2007ApJ...663.1187H} SN~Ia template at $B$-band peak as seen through our synthetic passbands,
$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.78\}$ and $b(U,B,V,R,I)=\{  1.64,   1.06,   0.16,  -0.40,  -0.52\}$ 
\color{black}
This linear approximation
is good in the ranges of
\color{red}
 $R^F_V$ and $A^F_V$,
\color{black}
and wavelengths under consideration, in that the values of the components  vary by $<5$\%.

@@

\color{red}
To help visualize the above result, Figure~\ref{plane:fig} shows two perspectives in $UVI$-space
of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model,
and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model.
The left plot shows that none of the four vectors are closely aligned with another, while the right plot shows that
the planes defined by our model (solid lines) and the  \citetalias{1999PASP..111...63F} model (dashed lines) are nearly coplanar.
If $R^F_V=2.4$ were constant in our sample, then $A_X = A_V\left(a(X) + \frac{b(X)}{2.4}\right)$;  this combination of $a$ and $b$ is
almost perfectly aligned with $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$, as shown in the dot-dashed line. 
\color{blue}
Note that the specific directions of $\gamma^0$ and
 $\gamma^1$  within their plane are based on the prior that $k_0$ and $k_1$ are uncorrelated.
\color{black}
The $\gamma^1$ terms capture the remaining magnitude variations due to the fact that $R^F_V$ is not constant in the sample:
if the $\gamma$'s are due to  \citetalias{1999PASP..111...63F} dust, the only way our analysis could recover
both $\gamma^0$ and $\gamma^1$ is for there to be variation in $R^F_V$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/plane0.pdf}
   \includegraphics[width=2.8in]{output11/plane1.pdf}
   \caption{
   \color{red}
   Two different perspectives in $UVI$-space of the vectors $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
   and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  The combination $a(X)+b(X)/2.4$ is shown in the dot-dashed
   line, almost perfectly superimposed on $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$.
   \color{black}
   \label{plane:fig}}
\end{figure}

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=4.5in]{output15/delta_corner.pdf}
   \caption{Significance of the non-zero values of $\delta$ seen through the posterior contours for $\delta$.  The bimodality is due to the degenerate solution due to sign change.
   \label{deltacorner:fig}}
\end{figure}

>>>>

\color{blue}
There remains degeneracies in the model.  One is illustrated by the  transformations $\Delta \rightarrow \Delta  + \epsilon_\Delta$,
 $\gamma^0 \rightarrow \gamma^0  + \epsilon_{\gamma^0}$, $\gamma^1 \rightarrow \gamma^1 + \epsilon_{\gamma^1}$under the condition
$$
\epsilon_\Delta  +  \epsilon_{\gamma^0} k_0+  \epsilon_{\gamma^1} k_1=0,
$$
i.e.\ shifts in the global coefficients $\gamma$ can be compensated by shifts in $\Delta$ for each supernova while maintaining 
$\langle \Delta \rangle=0$.
Another degeneracy is illustrated by $k_0 \rightarrow k_0 + (EW_{Ca}-\langle EW_{Ca}\rangle)\epsilon$,
$\alpha \rightarrow \alpha - \gamma \epsilon$, $c \rightarrow c + \langle EW_{Ca}\rangle \epsilon$, i.e. the
linear external terms can leak into the linear spectral feature corrections.
These degeneracies are not broken within the model, but rather are constrained by the priors, in which the
per-supernova parameters
$\Delta$, $EW$, $\lambda$, $k$ are uncorrelated.  It is important to emphasize that the latent parameters $k$ and $\Delta$
are non-trivially specified by these priors.
\color{black}

@@

The \citet{1989ApJ...345..245C} dust law can be expressed as a two-parameter linear model
\begin{equation}
A_X = a(X)  A_V + b(X) E(B-V).
\label{f99:eqn}
\end{equation}
The \citetalias{1999PASP..111...63F} model is approximately described by a linear model with
the above form:
\color{red}
for the case of
$R^F_V=2.5$ and $A^F_V=0.1$,
and the measurement of the updated
\citet{2007ApJ...663.1187H} SN~Ia template at $B$-band peak as seen through our synthetic passbands,
$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.78\}$ and $b(U,B,V,R,I)=\{  1.64,   1.06,   0.16,  -0.40,  -0.52\}$ 
\color{black}
This linear approximation
is good in the ranges of
\color{red}
 $R^F_V$ and $A^F_V$,
\color{black}
and wavelengths under consideration, in that the values of the components  vary by $<5$\%.

@@

\color{red}
To help visualize the above result, Figure~\ref{plane:fig} shows two perspectives in $UVI$-space
of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model,
and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model.
The left plot shows that none of the four vectors are closely aligned with another, while the right plot shows that
the planes defined by our model (solid lines) and the  \citetalias{1999PASP..111...63F} model (dashed lines) are nearly coplanar.

\color{blue}
Recall that degeneracies in the values of $\gamma$ and $k$ are broken by the prior that $k_0$, $k_1$, and the other SN parameters are uncorrelated. 
The combination  $\left(a(X) + \frac{b(X)}{2.4}\right)$ is
almost perfectly aligned with $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$ while $b$ alone is almost perfectly aligned with $\gamma^1_X/(\gamma^1_B-\gamma^1_V)$,
as shown in the dot-dashed and dotted lines of  Figure~\ref{plane:fig}.
Rewriting the \citetalias{1999PASP..111...63F} model in Eqn.~\ref{f99:eqn} as
\begin{equation}
A_X =  A_V^F\left(a(X)+\frac{b(X)}{2.4} \right) +  \left(\frac{ A_V^F}{R^F_V} - \frac{ A_V^F}{2.4}\right)b(X),
\end{equation}
we see the correspondence between $k_0$ with $A^F_V$, and $k_1$ with $\frac{A^F_V}{R^F_V}-\frac{A^F_V}{2.4}$.
Reasoning in the opposite direction, our results are motivated by a prior that ultimately turned out to be, based on our ultimate solution, 
\begin{align}
\text{cov}\left(A^F_V, \frac{A^F_V}{R^F_V}\right) & = \frac{1}{2.4} \text{var}(A^F_V).
\end{align}
Independent variations in $A^F_V$ and  $A^F_V/R^F_V$ within the data allowed the data analysis to detect
$\gamma^{0,1}$ and $k_{0,1}$ at high significance.
\color{black}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/plane0.pdf}
   \includegraphics[width=2.8in]{output11/plane1.pdf}
   \caption{
   \color{red}
   Two different perspectives in $UVI$-space of the vectors $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
   and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  The combination $a(X)+b(X)/2.4$ is shown in the dot-dashed
   line, almost perfectly superimposed on $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$, while $b(X)$ shown in the dotted line is
   almost  perfectly superimposed on $\gamma^1_X/(\gamma^1_B-\gamma^1_V)$.  
   \color{black}
   \label{plane:fig}}
\end{figure}

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=4.5in]{output15/delta_corner.pdf}
   \caption{Significance of the non-zero values of $\delta$ seen through the posterior contours for $\delta$.  The bimodality is due to the degenerate solution due to sign change.
 \color{blue}
 Three of the chains converged to one solution while the remaining chain converged to the other, resulting in the different normalizations of the two peaks.
 \color{black}
   \label{deltacorner:fig}}
\end{figure}
